---
title: "Untitled"
format:
  pdf:
    mainfont: Georgia
    monofont: Consolas
    linkcolor: Bittersweet
    citecolor: Mahogany
    urlcolor: MediumOrchid
    papersize: A6
    fig-format: png
    include-in-header:
      - text: |
          \usepackage[english,russian]{babel}
          \usepackage{fontspec}
          \setsansfont{Courier New}
          \usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools}
          \usepackage{icomma}
  html:
    theme: united
  beamer: 
    mainfont: Corbel
  pptx: 
    incremental: true
  revealjs: 
    incremental: true
  docx: 
    toc: true
  epub: 
    toc: true
bibliography: references.bib
---

## Знакомство с Quarto

Quarto позволяет нам сплетать вместе исполняемый код и изображения для создания чего-то там. To learn more about Quarto see <https://quarto.org>.

::: {.callout-note title="Обратите внимание"}
А это будет примечание
:::

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

See [@leontiev2011]
